```{r, echo = FALSE, warning = FALSE, message = FALSE}
source("header.r")
```

```{r}
cat("# Methods - ", .project, "\n")
cat("## Authors - ", .authors, "\n")
cat("## Date - ", .date, "\n")
```

## Introduction

Hierarchical Bayesian models were fitted to Kettle River snorkel data  using `r substr(R.version.string,1,15)` `r citep(.bib["r_core_team_r:_2013"])`
and JAGS 3.3.0 
`r citep(.bib["plummer_jags_2012"])` which interfaced with each other via the 
jaggernaut `r citep(.bib["jaggernaut"])` R package. For additional information 
on hierarchical Bayesian modelling in the BUGS language, of which JAGS uses a 
dialect, the reader is referred to `r citet(.bib["kery_bayesian_2011"])`.

Unless specified, the models assumed vague (low information) prior distributions `r citep(.bib["kery_bayesian_2011"], page = "36")`. The posterior distributions were estimated from a minimum of 1,000 Markov Chain Monte Carlo (MCMC) samples thinned from the second halves of three chains `r citep(.bib["kery_bayesian_2011"], page = "38-40")`. Model convergence was confirmed by ensuring that Rhat `r citep(.bib["kery_bayesian_2011"], page = "40")` was less than 1.1 for each of the parameters in the model `r citep(.bib["kery_bayesian_2011"], page = "61")`. The models are presented in the Models document.

The posterior distributions were summarised in terms of a point estimate (mean), lower and upper `r opts_jagr("level") * 100`% credibility limits (`r (1 - opts_jagr("level")) / 2 * 100`th and 
`r (1 - (1 - opts_jagr("level")) / 2) * 100` th percentiles), the standard deviation (SD), percent relative error (half the 95% credibility interval as a percent of the point estimate) and significance `r citep(.bib["kery_bayesian_2011"], page = "37,42")`.
The values are presented in the Results document.


The results are displayed 
graphically by plotting the modeled relationship between the particular 
variable(s) and the response (with `r opts_jagr("level") * 100`% 
credible intervals) while the 
remaining variables were held constant. In general, 
continuous and discrete fixed variables were held constant at their mean and 
first level values respectively while random variables were held constant at their 
typical values (expected values of the underlying hyperdistributions) 
`r citep(.bib["kery_bayesian_2011"], page = "77-82")`. Where informative the influence of particular variables is expressed in terms 
of the effect size (i.e., percent change in the response variable) with 
`r opts_jagr("level") * 100`% credibile intervals 
`r citep(.bib["bradford_using_2005"])`. Plots were produced using the ggplot2 R package `r citep(.bib["ggplot2"])`.
The plots are presented in the Figures document.


## Methods

The lineal density and observer efficiency were estimated from the snorkel count
and mark-resighting data for the Kettle River using a binomial mixture model `r citep(.bib["kery_bayesian_2011"], page = "383-388")`

Key assumptions of the binomial mixture model include:
* Detection probability is constant for all individuals.
* Lineal density varies randonly with year, site and site within year.
* There are no false positives such as double counts.

## References

```{r}
bibliography("html")
```
