```{r, echo = FALSE, warning = FALSE, message = FALSE}
source("header.r")
```

# Kettle River Rainbow Trout Snorkel Count Analysis 2013

## 6^th Jan 2014

*Suggested Citation: Thorley J.L. and Hogan P.M. (2014) Kettle River Rainbow Trout Snorkel Count Analysis 2013. A Poisson Consulting Ltd. Analysis. URL: https://github.com/poissonconsulting/kettle_snorkel_12.*

## Introduction

Hierarchical Bayesian models were fitted to Kettle River rainbow trout snorkel data  using `r substr(R.version.string,1,15)` `r citep(.bib["r_core_team_r:_2013"])`
and JAGS 3.3.0 
`r citep(.bib["plummer_jags_2012"])` which interfaced with each other via the 
jaggernaut `r citep(.bib["jaggernaut"])` R package. 

The data were provided by Redfish Consulting Ltd. with GIS and database support from Gary Pavan.

## Methods

Unless specified, the models assumed vague (low information) prior distributions `r citep(.bib["kery_bayesian_2011"], page = "36")`. The posterior distributions were estimated from a minimum of 1,000 Markov Chain Monte Carlo (MCMC) samples thinned from the second halves of three chains `r citep(.bib["kery_bayesian_2011"], page = "38-40")`. Model convergence was confirmed by ensuring that Rhat `r citep(.bib["kery_bayesian_2011"], page = "40")` was less than 1.1 for each of the parameters in the model `r citep(.bib["kery_bayesian_2011"], page = "61")`.

The posterior distributions are summarised in terms of a point estimate (mean), lower and upper `r opts_jagr("level") * 100`% credibility limits (`r (1 - opts_jagr("level")) / 2 * 100`^th and 
`r (1 - (1 - opts_jagr("level")) / 2) * 100`^th percentiles), the standard deviation (SD), percent relative error (half the 95% credibility interval as a percent of the point estimate) and significance `r citep(.bib["kery_bayesian_2011"], page = "37,42")`.

The results are displayed 
graphically by plotting the modeled relationship between the particular 
variable(s) and the response (with `r opts_jagr("level") * 100`% 
credible intervals) with the 
remaining variables held constant. In general, 
continuous and discrete fixed variables are held constant at their mean and 
first level values respectively while random variables are held constant at their 
typical values (expected values of the underlying hyperdistributions) 
`r citep(.bib["kery_bayesian_2011"], page = "77-82")`. Where informative the influence of particular variables is expressed in terms 
of the effect size (i.e., percent change in the response variable) with 
`r opts_jagr("level") * 100`% credibile intervals 
`r citep(.bib["bradford_using_2005"])`. Plots were produced using the ggplot2 R package `r citep(.bib["ggplot2"])`.

## Model Assumptions

The lineal density and observer efficiency were estimated from the snorkel count
and mark-resighting data for the Kettle River using a binomial mixture model `r citep(.bib["kery_bayesian_2011"], page = "383-388")`

Key assumptions of the binomial mixture model include:
* Lineal density varies randonly with year, site and site within year.
* Observer efficiency varies with discharge (a second order polynomial was considered
but was not significant and was excluded from the final model).
* Detection probability is constant for all individuals.
* There is no tag loss.
* Sites are closed between marking and counting.
* There are no false positives such as double counts.

## JAGS Code

JAGS distributions, functions and operators used in the models are defined in the following three tables. For additional information on the JAGS dialect of the BUGS language see the [JAGS User Manual](http://people.math.aau.dk/~kkb/Undervisning/Bayes13/sorenh/docs/jags_user_manual.pdf) `r citep(.bib["plummer_jags_2012"])`.

### JAGS Distributions

```{r}
mat <- matrix(
  ncol = 2,
  dimnames = list(NULL,c("Distribution","Description")),
  data = c("`dunif(a, b)`","Uniform distribution")
)

mat  <- rbind(mat,c("`dnorm(mu, sd^-2)`","Normal distribution"))
mat  <- rbind(mat,c("`dpois(lambda)`","Poisson distribution"))
mat  <- rbind(mat,c("`dbin(p, n)`","Binomial distribution"))
#mat  <- rbind(mat,c("`dbern(p)`","Bernoulli distribution"))
#mat  <- rbind(mat,c("`dlnorm(mu, sd^-2)`","Log-normal distribution"))
#mat  <- rbind(mat,c("`dcat(pi)`","Categorical distribution"))
#mat  <- rbind(mat,c("`ddirch(alpha)`","Dirichlet distribution"))
#mat  <- rbind(mat,c("`dgamma(shape, rate)`","Gamma distribution"))


mat <- mat[order(mat[,1,drop=T]),]

kable(mat)
```

### JAGS Functions

```{r}
mat <- matrix(
  ncol = 2,
  dimnames = list(NULL,c("Function","Description")),
  data = c("`log(x)`","Log of x")
)
mat  <- rbind(mat,c("`max(x,y)`","Maximum of `x` and `y`"))
mat  <- rbind(mat,c("`min(x,y)`","Minimum of `x` and `y`"))
mat  <- rbind(mat,c("`logit(x)`","Log odds of `x`"))
#mat  <- rbind(mat,c("`sum(a)`","Sum of elements of `a`"))
#mat  <- rbind(mat,c("`round(x)`","Round to integer away from `0`"))
#mat  <- rbind(mat,c("`T(x,y)`","Truncate distribution so that values lie between `x` and `y`"))

mat <- mat[order(mat[,1,drop=T]),]

kable(mat)
```

### JAGS Operators

```{r}
mat <- matrix(
  ncol = 2,
  dimnames = list(NULL,c("Operator","Description")),
  data = c("`<-`","Deterministic relationship")
)
mat  <- rbind(mat,c("`~`","Stochastic relationship"))
mat  <- rbind(mat,c("`x^y`","Power where `x` is raised to the power of `y`"))
mat  <- rbind(mat,c("`1:n`","Vector of integers from `1` to `n`"))
mat  <- rbind(mat,c("`a[1:n]`","Subset of first `n` values in `a`"))
mat  <- rbind(mat,c("`for (i in 1:n) {...}`","Repeat ... for `1` to `n` times incrementing `i` each time"))

mat <- mat[order(mat[,1,drop=T]),]
kable(mat)
```

## Model Code

The following sections provide the variable and parameter definitions and JAGS model code for the analyses. By convention variables are named using `CamelCase` and the number of levels of a discrete variable `Factor` is referenced by `nFactor`. 

```{r}
knit_models(.replacement)
```

## Parameter Estimates

The posterior distributions for the *fixed* (Kery and Schaub 2011 p. 75) parameters in each model are summarised below.

```{r}
knit_parameters(.replacement)
```


## Figures

```{r}
knit_figures(.replacement)
```


## References

```{r}
bibliography("html")
```
